% !TEX program = xelatex

\documentclass{resume}
\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Xinqi Chen (陈欣祺)}

\basicInfo{
  \email{chenxq66@sjtu.edu.cn} \textperiodcentered\ 
  \phone{(+86) 150-130-20347} \textperiodcentered\ 
  \address{吉林省长春市南关区国信中央新城一期}
}

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Shanghai Jiao Tong University (SJTU)} \hspace{2.1cm} Shanghai, China}{2021.09 -- Present}
\textit{Ph.D. student} in Computer Science (CS), expected to graduate in June 2026

GPA: 3.8/4.0 (Top 10\%)
\datedsubsection{\textbf{Sun-Yat Sen University (SYSU)} \hspace{3.4cm} Guangzhou, China}{2017.09 -- 2021.06}
\textit{B.S.} in Electronics Engineering (EE)

GPA: 3.9/5.0 (Top 10\%)

\section{\faUsers\ Experience}
\datedsubsection{\textbf{Alibaba Cloud, Elastic Block Storage Team} \hspace{1.2cm}  Hangzhou, China}{2023.09 -- Present}
\role{Alibaba Innovative Research Intern}{Advisor: Erci Xu}
Design and develop a proactive and reactive mixed scheduler named \textit{Omar} for the proxy layer in Alibaba Elastic Block Storage. \textit{Omar} can enhance tail latency performance by 60\% compared to existing solutions.

\datedsubsection{\textbf{Alibaba Cloud, Pangu AutoOps Team} \hspace{2.2cm} Hangzhou, China}{2022.07 -- 2023.09}
\role{Alibaba Innovative Research Intern}{Advisor: Erci Xu}
Design and develop an RL-based scheduler named \textit{MasterPlan} for archival storage systems. \textit{MasterPlan} can achieve
1.25$\times$ throughput and 1.47$\times$
power draw improvement compared to existing solutions.

\datedsubsection{\textbf{Pudu Robotics, Algorithm Development Team} \hspace{0.75cm} Shenzhen, China}{2020.10 -- 2021.01}
\role{Algorithm Development Intern}{Advisor: Cong Guo}
Develop a small object recognition algorithm for the delivery robot using RGB-D cameras. 
% \begin{itemize}
%   \item Implemented xxx feature
%   \item Optimized xxx 5\%
%   \item xxx
% \end{itemize}

% \datedsubsection{\textbf{xxx Projects}}{Jan. 2015 -- Present}
% \role{C, Python, Django, Linux}{Individual Projects, collaborated with xxx}
% Brief introduction: xxx
% \begin{itemize}
%   \item Implemented xxx feature
%   \item Optimized xxx 5\%
%   \item xxx
% \end{itemize}

% \datedsubsection{\textbf{\LaTeX\ résumé template}}{May. 2015 -- Present}
% \role{\LaTeX, Maintainer}{Individual Projects}
% An elegant \LaTeX\ résumé template, https://github.com/billryan/resume
% \begin{itemize}
%   \item Easy to be further customized or extended
%   \item Full support for unicode characters (e.g. CJK) with \XeLaTeX\
%   \item FontAwesome 4.5.0 support
% \end{itemize}

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faFileTextO \ Papers}
\begin{itemize}[parsep=0.5ex]
  \item \textbf{Xinqi Chen}, Weidong Zhang, Zhongyu Wang, Erci Xu, Dong Wu, Xiaolu Zhang, Haonan Wu, Yaheng Song, Chaolei Hu, Ruiming Lu, et al. Come for the QoS? Load Best Not Be Balanced! Scheduling Cloud Block Store Proactively and Reactively with
  Omar. (\textbf{In submission}). 2025.
  \item Lanqing Yang, \textbf{Xinqi Chen}, Hao Pan, Yi-Chao Chen, Guangtao Xue, Zechen Li, Yiheng Bian,
  Dian Ding, Linghe Kong, Jiadi Yu, Feng Lyu, Minglu Li, Ziyu Shen, and Bo Zhang. MagPrint++: Continuous User Fingerprinting On
  Mobile Devices Using Electromagnetic Signals. \textit{IEEE Transaction on Mobile Computing} (\textbf{CCF A, Major Revision}). 2025.
  \item \textbf{Xinqi Chen}, Erci Xu, Dengyao Mo, Ruiming Lu, Haonan Wu, Dian Ding, Guangtao Xue. MasterPlan: A Reinforcement Learning Based Scheduler for Archive Storage. \textit{ACM Transaction on Architecture and Code Optimization} (\textbf{CCF A}). 2024.
  \item Haonan Wu, Erci Xu, Ligang Wang, Yuandong Hong, Changsheng Niu, Bo Shi, Lingjun Zhu, Jinnian He, Dong Wu, Weidong Zhang, Qiuping Wang, Changhong Wang, \textbf{Xinqi Chen}, Guangtao Xue, Yi-Chao Chen, Dian Ding. Hey Hey, My My, Skewness Is Here to Stay: Challenges and Opportunities in Cloud Block Store Traffic. \textit{ACM EuroSys} (\textbf{CCF A}). 2024.
  \item Lanqing Yang, \textbf{Xinqi Chen}, Xiangyong Jian, Leping Yang, Yijie Li, Qianfei Ren, Yi-Chao Chen, Guangtao Xue, Xiaoyu Ji. Remote Attacks on Speech Recognition Systems Using Sound from Power Supply. \textit{USENIX Security Symposium} (\textbf{CCF A}). 2023.
\end{itemize}

\section{\faCogs\ Skills \& Languages}
\begin{itemize}[parsep=0.5ex]
  \item Skills: Python, C/C++, Golang, Latex, SQL, Shell, Linux, Docker
  \item Languages: Chinese (Native), English (CET-6 594)
\end{itemize}

% \section{\faHeartO\ Honors and Awards}
% \datedline{\textit{\nth{1} Prize}, Award on xxx }{Jun. 2013}
% \datedline{Other awards}{2015}

% \section{\faInfo\ Miscellaneous}
% \begin{itemize}[parsep=0.5ex]
%   \item Blog: http://your.blog.me
%   \item GitHub: https://github.com/username
%   \item Languages: English - Fluent, Mandarin - Native speaker
% \end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
